Fractional Types

### 2019-11-22 fracGC/p.tex
fix symbol
before merge
plan for 6.2

\newunicodechar{≟}{$\mathbin{\stackrel{?}{=}}$}
\newunicodechar{𝕌}{$\mathbb{U}$}
\newunicodechar{𝔹}{$\mathbb{B}$}
\newunicodechar{𝔽}{$\mathbb{F}$}
\newunicodechar{𝕋}{$\mathbb{T}$}
\newunicodechar{𝟘}{$\mathbb{0}$}
\newunicodechar{𝟙}{$\mathbb{1}$}
\newunicodechar{𝟚}{$\mathbb{2}$}
\newunicodechar{⋆}{${}_*$}
\newunicodechar{○}{$\gcv$}
\newunicodechar{ᵤ}{${}_u$}
\newunicodechar{⊚}{$\fatsemi$}
\newunicodechar{⟷}{$\leftrightarrow$}
\newunicodechar{⟶}{$\longrightarrow$}
\newunicodechar{⟪}{$\ll$}
\newunicodechar{⟫}{$\gg$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{ₗ}{$_l$}
\newunicodechar{ᵣ}{$_r$}

@@

%%%%% 
\subsection{Pointed Types}

 rationale: we want singleton types to track, in the type system
the values of ancillae, i.e.. we construct a proof using the type
system. Technically the singleton types allow you to focus on one
value by reflecting it in the type system. Now this type can only be
equal to another type if and only if the other type is the same
singleton value.

Once singleton types are built, we need to make sure circuit
evaluation is also reflected in the type system. So in fact
computation itself is reflected in the type system. In order to mix
singleton types with other types, we use pointed types as a unifying
substrate. Now all types have values; we can focus (using monad) and
unfocus using (comonad). (This by the way ensures we don't write 1/0
which would be bad).

%%%%% 
\subsection{Singleton Types}

Consider the type $\Sigma \mathbb{N} (\lambda n. n \equiv 5)$. Values
of that type are a number $m$ and a proof that this is number is equal
to 5. So we can have $(4 + 1, \textit{refl})$, $(2 + 3 ,
\textit{refl})$, and so on. All these syntactically different values
are identical to 5 and hence we can \emph{contract} the type to a
single point at 5.

PiPointedFrac:
lift pi
lift multiplicative structure
monad/comonad for singletons
eta/epsilon

@@

RECIP

Combinators:
\PIPFCombDef{}

@@

>>>>

\newunicodechar{≟}{$\mathbin{\stackrel{?}{=}}$}
\newunicodechar{𝕌}{$\mathbb{U}$}
\newunicodechar{𝔹}{$\mathbb{B}$}
\newunicodechar{𝔽}{$\mathbb{F}$}
\newunicodechar{𝕋}{$\mathbb{T}$}
\newunicodechar{𝟘}{$\mathbb{0}$}
\newunicodechar{𝟙}{$\mathbb{1}$}
\newunicodechar{𝟚}{$\mathbb{2}$}
\newunicodechar{⋆}{${}_*$}
\newunicodechar{○}{$\gcv$}
\newunicodechar{ᵤ}{${}_u$}
\newunicodechar{⊚}{$\fatsemi$}
\newunicodechar{⟷}{$\leftrightarrow$}
\newunicodechar{⟶}{$\longrightarrow$}
\newunicodechar{⟪}{$\ll$}
\newunicodechar{⟫}{$\gg$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{ₗ}{$_l$}
\newunicodechar{ᵣ}{$_r$}
\newunicodechar{❰}{$\llparenthesis$}
\newunicodechar{❱}{$\rrparenthesis$}

@@

%%%%% 
\subsection{Pointed and Singleton Types}

@@

Combinators:

\PIPFCombDef{}

properties of singleton, recip  
derive join etc  
monad,comonad structure

@@

show a small example
